Projit: An Open Source tool for Decoupled Data Science

### 2023-06-19 docs/paper/paper.tex
Paper updates

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Decoupled Data Science - Tools for flexible, reproducible eScience}

@@

\begin{abstract}
\end{abstract}

%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003260.10003261</concept_id>
<concept_desc>Information systems~Web searching and information discovery</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002951.10003260.10003277.10003280</concept_id>
<concept_desc>Information systems~Web log analysis</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010257</concept_id>
<concept_desc>Computing methodologies~Machine learning</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Web searching and information discovery}
\ccsdesc[500]{Information systems~Web log analysis}
\ccsdesc[500]{Computing methodologies~Machine learning}

@@

We begin by discussing all desirable elements required of an open science framework. These are drawn
from observations of both how collabroative science works and the successful components of distributed
scientific endeavours. These requirements are drawn from both sciences that are typically dependent
on computational frameworks (computer science, bioinformatics, physics) and those that generally are not
(social science, psychology).

@@

\begin{itemize}
 \item Provenance of Data Sources
 \item Record of Data Processing
 \item Reuse of Datasets
 \item Tracking of Experiments and Results
 \item Comparison of Methods and Results
 \item Generation of Documentation
 \item Reproducibility of Projects
 \item Facilitation of Meta-Analysis
\end{itemize}

\subsection{Data}

\subsection{Features}

\subsection{Feature Importance}

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Projit: An Open Source tool for Decoupled Data Science}

@@

\begin{abstract} 
Scientific practice has expanded to become increasingly dependent of digitial technologies,
large scale data processing and advanced analytical methods. These shifts have demanded new
methods of implementing and recording the details of scientific projects. Monolothic applications
have the advantage of a single and consistent design, however they impede the ability of users to
innovate and incrementally improve processes. We discuss the qualities of an ideal eScience framework
for building multi-stage collaboration scinetific workflows and present an open source implementation
for managing scientific processes in a decoupled fashion that permits both flexible implementation of
any stage of processing, and greater ease of meta-data analysis.
\end{abstract}

@@

We begin by discussing all desirable elements required of an open science framework. These are drawn
from observations of both how collaborative science works and the successful components of distributed
scientific endeavours. These requirements are drawn from both sciences that are typically dependent
on computational frameworks (computer science, bioinformatics, physics) and those that generally are not
(social science, psychology).

@@

\begin{itemize}
 \item Sources: Provenance of Data Sources
 \item Processing: Record of Data Processing
 \item Reuse: Facilitating Reuse of Datasets
 \item Tracking: Tracking of Experiments and outputs
 \item Results: Comparison of Methods and Results
 \item Documentation: Generation of Documentation
 \item Reproduction: Reproducibility of Projects
 \item Meta-Analysis: Facilitation of Meta-Analysis
\end{itemize}

The elements in this list are organised in an approximately sequential manner. However, as we discuss
them below it should be apparent that there are many ways in which these elements support each other.
Firstly, and foremost, aata driven projects
require a method of accessing the required \textbf{source} data and will need to maintain records 
of this data provenance. There will typically be \textbf{processing} applied to these datasets to 
render them applicable to experimentation and analysis. An ideal tool will track the sequential 
nature of this processing as well as store information about the location of each resulting dataset.
The data processed in this way is then available for \textbf{reuse} across experiments and analysis,
making \textbf{results} comparable and facilitating \textbf{meta-analysis}.

\subsection{Projit Process}

The central design principle of \textit{projit} is that the decoupling of data science 
should be achieved through utilisation of a simple metadata store. Each aspect of 
data science work can be allowed to proceed without awareness of the structure of 
any other element as long as it can access the information it requires through this
metadata store.

\begin{figure*}
\includegraphics[scale=0.6]{./Projit_decoupled_process.drawio.png}
\caption{Projit Process for Decoupled Data Science}
\label{fig:projit}
\end{figure*}

In Figure \ref{fig:projit} we see that the core steps of data preparation, experimentation
and analysis of results all happen independently. Each of them accesses the projit store for
the information they need, storing information

\subsection{Application}
